\subsection{Group Organization}

In this project we are only 4 people and that will affect how we organize 
the group. We will try to assign roles and responsabilities, but it will
require that each group member has more than 1 role.
In scrum there are mainly 3 roles: product owner, scrum master and the
scrum team. Since we are a small group we will have a overall flat structure. That means that
there will be traditionally project roles that will not be assigned to a specific person, 
but to the group as a whole. It will be the project managers responsability to ensure 
that activities within a unassiged role are covered during the project.

\subsubsection{Roles}

{\bf The Scrum Master (Project manager)} is the responsible person for the progress of the project 
as well as having control on the organizational tasks like planning and workload.
To keep the righ direction of the project, the project manager has to make plans for 
activities like sprints, meetings and deliveries. This include contact with customer and the supervisor.
Before every sprint, meeting and delivery, the project manager has the responsability to book a room, contact all
participants as well as creating the agenda for the meeting. \\

\noindent
{\bf The Scrum Team}
\begin{itemize}

  \item {\bf Test manager:} has the role to ensure the quality of the product. To keep the quality 
  of the product, the test manager has to ensure that each developer create unittests for the 
  produced code, ensure that all the planned test activities is performed and that the results 
  from all test activities is reported.

  \item {\bf Document owner:} has the responsability to allocate task to all the group members so we can meet the deadlines. The document owner does also have the responsability the keep track of what setions in the report to deliver in each sprint and the quality of what we deliver.

  \item {\bf Technical leader:} has the role to ensure that the right technology is
  chosen, have the overview of the version control sytstem and training the group members
  in the technology needed.

  \item {\bf Development leader:} has the responsability to ensure that we will meet our goals
  for each sprint and that each developer are doing their tasks. The goals are described in each 
  sprint as "features to implement". 

  \item {\bf Developer:} each developer has the responsability to produce quality code
  and write unittest for what he/she produce. Every developer do also have the responsability
  to make sure that the produced code that is pushed to the repository is running and working
  according to the requirement specification.
  \end{itemize} 

\subsubsection{Allocation of roles}
In this project, every member has a role with responsability described in the section above ("Roles").
The roles we had chosen were selectecd were chosen based on our need in the project. 
Since we are a small group, we did not want to have too many roles.

There will always be small roles to fullfill, but we will not allocate all the roles in details, 
but try to hav a responsible person for the critical parts in the project.
If a roles needs to be allocated during the project, it will be the project managers job to
allocate this.

The roles were allocated during a group meeting:
\begin{itemize}
  \item The Scrum Master (Project manager): Marte Løge
  \item Test manager: Solveig Hellan
  \item Document owner: Solveig Hellan
  \item Technical leader: Anders Wold Eldhuset
  \item Development leader: Martin Stølen
  \item Developer: Marte Løge, Solveig Hellan, Anders Wold Eldhuset and Martin Stølen
\end{itemize}





