\subsection{Project Phases}

In this project will we work in phases called sprints.
In the first period did we work in a 2weeks period where we had our preliminary study and planning. The next periods are the sprints (1-4). These periods are scheduled to last for 2 weeks each with focus on the implementation of the game. The last phase are the delivery and documentation pahse. In this phase we are not implementing any new features, but are going to ensure that all code we have produced are ready for delivery as well as finish our report.

\subsubsection{Planning and research}
In this phase we did have the focus on getting startet. Every project need roles, a plan and a description of what to deliver. We started with delegate roles. After delegating roles we had to get started with the game concept as well as a make a requirement specification. 

When we had decided on what game to make and which features to deliver, we had to decide what technology to use, what methodology to follow as well as making an overall project plan. 

\subsubsection{Sprints}
This phase of the project is divided into 4 phases that we call sprints that lasts for 2 weeks.
In the sprints the focus is on what features to deliver in the end of the sprint as well as 
making progress with the report. The activities and the results in each sprint is described as
own chapters in this report.

\subsubsection{Documentation and delivery}
This phase is the last week of the project. This is the time where we dont implement any new features, 
but make the game stable and playable. It is also important to make the final documentation in this phase.
