\section{Stakeholders}

A stakeholder is a person or organization that has an interest in the project. They may be actively involved in the project, affected by the execution or completion of the project, or have an influence on the project objectives and outcome. Four stakeholders have been identified. \cite{stakeholder}


\paragraph{Project Team}

The project team consists of the four students that form group number 10 listed in Table 1.1. The project team is concerned with fulfilling the requirements of the product within the given time frame, and satisfying the expectations of the customer.

\definecolor{gray}{gray}{0.6}

\begin{table}[H]
\begin{center}
    \begin{tabular}{| l | l |}
   	\hline
    \rowcolor{gray}
    {\bf Name} & {\bf E-mail} \\ \hline
    Marte Dybevik Løge & martedl@stud.ntnu.no \\ \hline
    Martin Stølen & martstol@stud.ntnu.no \\ \hline
    Anders Wold Eldhuset & andereld@stud.ntnu.no \\ \hline
    Solveig Hellan & solvehel@stud.ntnu.no \\ 
    \hline
    \end{tabular}
\end{center}

\caption{Project Team}
\end{table}

\paragraph{Customer}

As stated above the customer is the market division of Helgelandskraft, represented by Arild Markussen and Espen Skarsbø Olsen. The customer will evaluate the product on regular intervals throughout and at the end of the project. The customer is concerned with receiving a product that meets their expectations and fulfills their requirements. The customers are listed in Table 1.2.

\begin{table}[H]

\begin{center}
    \begin{tabular}{| l | l |}
   	\hline
    \rowcolor{gray}
    {\bf Name} & {\bf E-mail} \\ \hline
    Arild Markussen & arild.markussen@helgelandskraft.no \\ \hline
    Espen Skarsbø Olsen & espen.olsen@helgelandskraft.no \\
    \hline
    \end{tabular}
\end{center}

\caption{Customer}
\end{table}

\paragraph{Advisor}

The advisor is concerned with keeping an eye on the process of the project, the dynamic in the group and making sure that contact with the customer is being maintained. The advisor is listed in Table 1.3.

\begin{table}[H]

\begin{center}
    \begin{tabular}{| l | l |}
    \hline
    \rowcolor{gray}
    {\bf Name} & {\bf E-mail} \\ \hline
    Tosin D. Oyetoyan & tosindo@idi.ntnu.no \\
    \hline
    \end{tabular}
\end{center}

\caption{Advisor}
\end{table}

\paragraph{End Users}

End users will evaluate the product throughout the project. The feedback the end users provide will influence the final product.


