\chapter{Glossary}


\begin{description}
   \item[AgileZen] A web-based application for project management based on agile methodologies.
   \item[Android] A mobile operating system.
   \item[Android Debug Monitor] Also called Dalvik Debug Monitor Server. Provides port-forwarding services, screen capture on device, thread and heap information, logcat, incoming call and SMS spoofing, etc.
   \item[Android Virtual Device] A device configuration that is run with the Android emulator.
   \item[Backbone.js] A JavaScript library for structuring javascript code.
   \item[CMS] Construction and Management Simulation, a game in which players manage communities or projects with limited resources.
   \item[CSS] Cascading Style Sheets, a style sheet language used for describing the presentation semantics of an application.
   \item[Dropbox] A web-based file hosting service.
   \item[Gantt diagram] A chart that illustrates a project schedule.
   \item[Git] A distributed version control system.
   \item[GitHub] A web-based hosting service for software development project, using Git for version control.
   \item[GUI] Graphical User Interface, allows users to interact with devices through graphical elements.
   \item[HTML] HyperText Markup Language, markup language for creating web pages and applications.
   \item[HUD] Heads Up Display, any transparent display that presents data without requiring users to look away from their usual viewpoints.
   \item[iOS] A mobile operating system developed by Apple.
   \item[JavaScript] A programming language.
   \item[jQuery UI] A JavaScript library for easily handling common user interactions and visual effects.
   \item[LaTex] A document preparation system and document markup language.
   \item[Native] Targeted at one specific platform (in the context of software development).
   \item[Phonegap] A mobile development framework, allowing programmers to build applications for mobile devices using JavaScript, HTML, and CSS.
   \item[Scrum] An iterative and incremental methodology for managing software projects.
   \item[SDK] Software Development Kit, a set of software development tools that allows for the development of applications.
   \item[Skype] A voice-over-IP service and instant messaging client.
   \item[Sprint] A time-limited period of work, with a delivery at the end, in the Scrum methodology.
   \item[Sprint Backlog] The list of work a team must address during the next sprint.
   \item[UML] Unified Modeling Language, a standardized, general-purpose modeling language in software engineering.
   \item[Underscore.js] A JavaScript library with support for many functional programming idioms.
   \item[Waterfall] A sequential methodology for managing software projects.
\end{description}
